The Inconsistency in G\"odel's Ontological Argument: \\ A Success Story for AI in Metaphysics

### 2016-01-31 Papers/InProgress/IJCAI/submission.tex
Improve conclusion

\section{Conclusion}\label{sec:conclusion}
The axioms and definitions in G\"odel's manuscript are inconsistent;
this has been detected automatically by the prover
\textsc{Leo-II}. Here we have presented a rational reconstruction and
verification of the inconsistency argument in Isabelle/HOL. This
argument is valid in all normal HOMLs including base logic \K.

We have also presented several technical improvements regarding the
semantic embedding approach. In particular, we have a achieved a
nearly perfect match between pen and paper presentations in HOML and
the syntax in Isabelle/HOL. As a result, the embedding of HOML in HOL
is now fully transparent and ready for wider adoption by
philosophers.

@@

Another open problem that we solved in this paper is a fully automatic
proof of T3 directly from Scott's axioms. Again, this proof was
contributed by \textsc{Leo-II}. However, this has been possible only
after providing a more efficient embedding for HOML \textbf{S5} in HOL.

Both the automated detection of the inconsistency in G\"odel's axioms
and the fully automatic proof of T3 from Scott's axioms demonstrate
the potential of our AI technology for philosophy: this technology is
in its current state of development already capable of contributing novel results to
metaphysics and to conduct reasoning steps at granularity-levels
beyond common human capabilities.  % ToDo: or even Gödel-level capabilities :-)

>>>>

\section{Conclusion}\label{sec:conclusion}

The axioms and definitions in G\"odel's manuscript are inconsistent;
this was detected automatically by the prover
\textsc{Leo-II}. Here we presented a rational reconstruction and
verification of the inconsistency argument in Isabelle/HOL. This
argument is valid in all normal HOMLs including base logic \K.

We have also presented several technical improvements regarding the
semantic embedding approach. In particular, we have achieved a
nearly perfect match between pen and paper presentations in HOML and
the syntax in Isabelle/HOL. As a result, the embedding of HOML in HOL
is now fully transparent, more user-friendly and ready for wider adoption.

@@

Another open problem that we solved in this paper is a fully automatic
proof of T3 directly from Scott's axioms. Again, this proof was
contributed by \textsc{Leo-II}. This has become possible only
after we provided a more efficient embedding for HOML \SFiveU (instead of \SFive) in HOL.

Both the automated detection of the inconsistency in G\"odel's axioms
and the fully automatic proof of T3 from Scott's axioms demonstrate
the potential of our AI technology for philosophy: this technology is,
in its current state of development, already capable of contributing novel results to
metaphysics and to conduct reasoning steps at granularity-levels
beyond common human capabilities.  % ToDo: or even Gödel-level capabilities :-)
